### 2020-03-27 spores-protocol-paper/reviews/rebuttal-ndss.md

We would like to thank the reviewers for their constructive reviews. We structured our response by topic, referring to reviewers as RA and RB.

We agree with your joint suggestions for presentation (operational diagram, roles of protocols/subsystems; overview in text, details in appendix) and reference to Weiser; we will update the paper accordingly.

Regarding the concern about privacy threats from availability prediction data: @RB the data used for prediction is stored locally, only the predicted availability can be sampled. 
@RA leaks from prediction are analyzed in Section VI  (Device unlinkability), albeit for the worst case of extremely detailed availability data. In practice, leaks are constrained by separate address spaces (NFC for the out-of-band set-up step, and IP for availability sampling), public keys which can be replaced regularly, and availability prediction being coarse-grained and thus not unique. There are corner cases that allow for a link between IP addresses and devices and then potentially owners; for example when the adversary is behind the same NAT as the target, but even those are short-lived due to the coarse-grained prediction.

@RB on onion routing without circuits: this is likely a terminology issue. Onion routing is associated with circuits as Tor uses them, but it is not included in the definition in reference [21].  While Tor establishes circuits by maintaining a routing table at relays according to the onion layers, SphinxES (and Sphinx) defines a header format that encapsulates the routing information, hence the statelessness of SP²ORES.

@RB about global v. local sampling, we sample globally to achieve anonymity: if we only used our own devices, we would expose whom we are communicating with through our network metadata and Alice would reveal her devices to Bob.

Both reviewers expressed concerns regarding the realism of our evaluation. We have considered data collections such as Crawdad, but the data sets are not applicable as-is to our problem. Mobility is not a direct estimator of availability (e.g. mobile phones are available even during transitions), and it does not capture the interaction of a user with several of her devices, an emergent domain for which field data does not exist yet. We will keep an eye on data collections for any more directly applicable traces or empirical studies on availability of devices and their relation to data on mobility and other traces.

In the absence of data, HMM are commonly used for simulating user behavior. Should user behavior diverge markedly, however, the prediction module we use (based on plain Markov Chains) could be exchanged for one adapted to the scenario, for instance using privacy-preserving decentralized machine learning [Bellet, Guerraoui, et al, 2018].

@RB We agree that adapting our Docker setup to emulate more complex network properties and energy constraints could enrich our model. Our choice was to fold issues of network reliability and device resources together with device availability, considering that a poorly connected device is in effect only intermittently available. We believe that this provides an appropriate approximation for our experimental aims.

#Wannabe final version:

We would like to thank the reviewers for their constructive reviews. We structured our response by topic, referring to reviewers as RA and RB.

We agree with your joint suggestions for presentation (operational diagram, roles of protocols/subsystems; overview in text, details in appendix) and reference to Weiser; we will update the paper accordingly.

Regarding the concern about privacy threats from availability prediction data: @RB the data used for prediction is stored locally, only the predicted availability can be sampled. 
@RA leaks from prediction are analyzed in Section VI  (Device unlinkability), albeit for the worst case of extremely detailed availability data. In practice, leaks are constrained by separate address spaces (NFC for the out-of-band set-up step, and IP for availability sampling), public keys which can be replaced with configurable frequency, and availability prediction being coarse-grained and thus not unique. There are corner cases that allow for a link between IP addresses and devices and then potentially owners; for example when the adversary is behind the same NAT as the target, but even those are short-lived.

@RB on onion routing without circuits: this is likely a terminology issue. Onion routing is associated with circuits as Tor uses them, but it is not included in the definition in reference [21].  While Tor establishes circuits by maintaining a routing table at relays according to the onion layers, SphinxES defines a header format that encapsulates the routing information, hence the statelessness of SP²ORES.

@RB about global v. local sampling, we sample globally to achieve anonymity: if we only used our own devices, we would expose whom we are communicating with through our network metadata.

Both reviewers expressed concerns regarding the realism of our evaluation. We have considered data collections such as Crawdad, but the data sets are not applicable as-is to our problem. Mobility is not a direct estimator of availability (e.g. mobile phones are available even during transitions), and it does not capture the interaction of a user with several of her devices, an emergent domain for which field data does not exist yet. We will keep an eye on data collections for any more directly applicable traces or empirical studies on availability of devices and their relation to data on mobility and other traces.

In the absence of data, HMM are commonly used for simulating user behavior. Should user behavior diverge markedly, however, the prediction module we use (based on plain Markov Chains) could be exchanged for one adapted to the scenario, for instance using privacy-preserving decentralized machine learning [Bellet, Guerraoui, et al, 2018].

@RB We agree that adapting our Docker setup to emulate more complex network properties and energy constraints could enrich our model. Our choice was to fold issues of network reliability and device resources together with device availability, considering that a poorly connected device is in effect only intermittently available. We believe that this provides an appropriate approximation for our experimental aims.

-------------

[If room: In addition, devices in proximity can more easily be controlled by the same entity, thus they can more easily collude to de-anonymize the connections.]

Both reviewers expressed concerns regarding the realism of our evaluation. Mobility/connectivity datasets are not applicable as-is to our study, because they do not capture the interaction of a user with many of her devices, an emergent domain for which field data does not exist yet.
There are not a direct mapping between mobility and availability.... Mobility is not a direct indicator about availability ... Mobility is not a direct estimator of availability 
 Still, we thank you for the Crawdad pointer. OR We keep an eye on Crawdad in the hope that some dataset would be directly applicable to our work.
 [If room: we would need to make our own empirical study/a contribution.]

@RA <insert separated address spaces, short-lived public keys, coarse-grained availability, point to device unlinkability, still corner cases left that can link IP to device/owner [We must state clearly that most of the time [we don't know if it's most of the time], we **cannot** link IP to owner]>.

In the absence of data, HMM are commonly used for simulating user behavior. Should user behavior diverge markedly, however, the prediction module we use (based on plain Markov Chains) would be enriched, for instance using privacy-preserving decentralized machine learning [Bellet, Guerraoui, et al, 2018].

@RB on onion routing without circuits: this is likely a terminology issue. Onion routing is associated with circuits as Tor uses them, but it is not included in the definition in reference [CL]. Sphinx is a header format for mix networks, and SP2ORES is technically a source-bounded random walk that adapts sphinx headers for encapsulating routing information (onion routing) per packet (SP2ORES, not IP) and not per connection (circuit).
but it is not mandatory according to [CL]. While Tor pre-establishes circuits by maintaining a routing table at relays, Sphinxes defines a header format that contains all the routing information, hence the statelessness of SP²ORES.
[Encrypted Tor packets == *cells*]

We therefore simulated user behavior using Hidden Markov chains, because of [versatile/widely used/ simplicity and realism [Gambs, Killijian, Núñez del Prado Cortez, 2012]

#Answers to questions

We merged all these issues by exhibiting different levels of availability.

###- Q1,RA: Location privacy, how much info is leaked by the published prediction?

We have an implicit assumption that when Alice and Bob communicate
out-of-band they use local addresses which are unlinkable to the
addresses used on the global network (\ie where they advertise P'd).

I remember this as being emphasized in the paper, but now that I read
the system model it's very implicit. This should be fine: they use IP
for global communication and bluetooth or NFC for out-of-band. These are
different address spaces, hence according to our assumption.

We also (implicitly) assume that the network addresses are independent
of the owner's attributes --- this should be emphasized in the paper!

This is not the case for IP: GeoIP services work for this reason. \Eg if
Bob knows where Alice lives he can use GeoIP to look for IPs that are
likely Alice's. Also if Alice and Bob are on the same NATed LAN, they
will have the same global address. Then Bob can read out every entry in
the RPS that has the same IP as himself. If there are only two and he
knows that Alice is also using the service (likely if she's exchanging
out-of-band data with him), then he can be quite certain that that's
Alice. Then if the probability is quite unique he can use that as
Alice's identifier, \ie he can track her addresses later (and use GeoIP
to follow her location).

In that sense, it's better for Alice to use her 4G connection instead of
local WiFi. Since then Bob cannot know her address on the global network
--- only that she's online (this case is analysed in the security
discussion, see "Device unlinkability" there). Of course, then her
ISP/phone carrier can learn her online behaviour, but they do that
anyway. Maybe the device-to-device of 5G will break this property for
Alice.

###- Q2,RB: It's unclear how onion routing is used without circuits:

This is a problem with terminology. There's first that CL called it
onion routing. Sphinx is a mixnet header. SphinxES is too. Technically,
routing is something stateless: there are no circuits in IP. We route
packets through multiple layers, using multiple layers of encryption,
hence onion routing. The problem is that, right now, onion routing is
synonymous to Tor. Tor sets up a state at each
node, \ie the circuit setup. We contain all that data in the header of
each packet, this is inherited from mixes. This gives us larger overhead
than Tor, as Tor can send just data without headers after the circuit
setup.

So we're correct in calling it onion routing. On the other hand we're
closer to a mix-cascade in that sense, except we don't do batching,
which is characteristic for mixes. Strictly speaking, using that survey
I used to characterize our work (of which I'm not sure how much remains
in the paper), we're technically a "source-routed bounded random-walk",
or maybe "source-bounded random-walk" is better.

###- Q3,RB: How are the overheads in terms of data transmitted and power used by this system for the small personal devices people keep with them?

I don't think processing one packet is much more expensive than an HTTPS handshake. But it's of course better to know, or at least make the estimate more explicit.

###Q4,RB: Why have a global DHT with all devices instead of choosing locally?

We use  a global DHT to achieve anonymity: if we only used our own devices, we would expose whom we are communicating with through our network metadata. In addition, devices in proximity can more easily be controlled by the same entity, thus they can more easily collude to de-anonymize the connections.

###- Q5,RB: Isn't the data needed for the prediction privacy sensitive, wouldn't the system endager users' privacy?
The data doesn't leave the user's own devices. The only data that leaves is in "aggregate from" in terms of the prediction. This information can be very coarse-grained, which it is in our evaluation.

###- Q6, RA, RB:  Both reviewers expressed concerns regarding the realism of our evaluation.

(See text above)

----
v2:
We use a general model for our predictions: a Markov chain (not Hidden) where states are the bitarray denoting which devices are connected: our prediction of a future device's availability solely depends on which devices are online now, given the history of the user's behavior. Our argument is that prediction enables onion routing. If we had field data, we would choose another prediction model, e.g. Recurrent Neural Networks, that are good candidates for classifying patterns in time series.
For the evaluation, we introduced the user's location (leading to a HMM), which enabled to model fixed appliances tied to a location (i.e. more realistic connection traces than mere random).
Despite the location transition matrix being fixed for all users, devices' connectivity traces exhibit much diversity, because the number, type and connection probability of devices are all different for each user.

Our study did not consider connection unreliability or devices' scarce resources, because we collapsed these concepts with device availability: a user carrying their phone outside would have e.g. 65% of availability, because the phone's connection often drops and its resources are constrained. Using Docker to limit the resources of devices, or simulate an unreliable network with high latency would still benefit the soundness of our experiments, but certainly field data would be best.
Mobility/connectivity datasets are not applicable as-is for our study, because they do not capture the interaction of a user with many of their devices; we would need to engage in empirical experiments to get data on the emerging trend of e-squads.
Still, studies about user mobility prediction (like \url{https://crawdad.org/yonsei/lifemap/20120103/)} or connectivity over time are of interest to us, and we thank you for pointing us to Crawdad.

-----
v1:
We use a general model for our predictions: a Markov chain (not Hidden) where state are the bitarray stating which devices are connected:
our prediction of a future device's availability solely depends on which devices are online now, given the history of the user's behavior.
For the evaluation, we introduced a second stochastic process, the user's location, which enabled to model fixed appliances tied to a location.
Despite the location transition matrix being fixed for all users, devices' connectivity traces exhibit much diversity, because the number, type and connection probability of devices are all different for each user. 
We picked a Markov prediction model because it fits the simulated users behavior. If we had field  but we would strengthen our prediction with a more complex model if we had different (real world) traces of human behavior (e.g. Recurrent Neural Networks are good candidates for classifying patterns in time series).
Which leads to the question of ground data being absent from our experiments.
Mobility/connectivity datasets are not applicable as-is for our study, because they do not capture the interaction of a user with many of their devices; we would need to engage in empirical experiments to get data on the emerging trend of e-squads.
Still, studies about user mobility prediction (like \url{https://crawdad.org/yonsei/lifemap/20120103/)} or connectivity over time are of interest to us, and we thank you for pointing us to Crawdad.
Lastly, our study did not consider connection unreliability or devices' scarce resources, because we collapsed these concepts with the availability: 
a user carrying their phone outside would have e.g. 65% of availability, because the phone's connection is often dropping and its resources are constrained.
Using Docker to limit the resources of devices, or simulate an unreliable network with high latency would still benefit the soundness of our experiments.

#Adrien V1

Dear Reviewers,

Thank you for valuable comments! Notably, we understand that the relationship between SP²ORES' building blocks must be better explained (with a figure), that putting SphinxES details (Section IV) in an appendix would facilitate the presentation, and that we need to address the security risks of publicly advertising the devices' predicted availability.

We will develop on two other points: the statelessness of SP²ORES, and our evaluation testbed.

Reviewer B observed the following: "It is not clear how you use onion routing without circuits". 
In Tor, Alice creates onion routes by iteratively contacting her designated relays. The Onion Routers (OR) along the path must remember where to forward each received stream (i.e. they maintain a routing table).
Unlike it, SP²ORES builds routes by crafting a self-sufficient header beforehand, such that each OR will know where to forward each packet by simply decrypting the header.
// To enjoy sender-receiver anonymity in SP²ORES, both ends of the circuit must exchange their headers out-of-band.

You coined our evaluation optimistic, and doubted its realism. It is true that we only employ fabricated user traces (furthermore, using the same stochastic model as our prediction engine).
We aim to show that, assuming information on personal devices (such as timestamped connection/disconnection), it is possible to infer their future availability by modeling the user's behavior. 
Alas, real-world data that would fit our purpose is cruelly lacking (at least for academia). Adapting data such as wireless connectivity traces to fit our purpose (multi-device interaction over time) would by itself constitute a legitimate contribution: we firmly envisage to tackle it in the near future.

##Quotes from reviewers

###On the evaluation.

since human movements are emulated in the evaluation via a Hidden Markov Model
(HMM) and HMMs also serve as the models as to how SP$^2$ORES forms
predictive behavior.  In other words, the evaluation uses a model
that's assumed by the implementation, and thus misses how actual human
behavior (which doesn't strictly conform to HMMs) affects performance.
# @B Section VII I wonder how realistic the performance 
evaluation is. I would have liked some discussion of how the Docker instances 
can be limited to emulate lower powered devices. Also, how do you distribute 
the user's e-squads over the five machines in your evaluation. I feel like 
putting these all on the same machine will hide impacts of unreliable wireless 
channels on your results. 
# @B Section VII It would have been nice to see models of user 
mobility that are available in existing traces vs. a totally simulated 
mobility/usage pattern here. E.g., traces from CRAWDAD (\url{https://crawdad.org/)} 
may be a good starting point to create more realistic user models.

### 2020-03-27 paper/sphinxes.tex

\section{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
Sphinx only provides one node per onion layer; in this section we extend Sphinx 
to \Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

\begin{figure}
  \centering
  %  \includegraphics[width=\linewidth]{figures/OR-POR.png}
    \includegraphics[width=0.65\linewidth]{figures/principle_SPOR.pdf}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing 
and mixing (OR, top) and \ac{SPOR} (bottom).
    %\commentDaniel{This figure should be fixed, issue \#42.}
  }
\end{figure}

\subsubsection{Overview of the Sphinx header format}

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

\subsubsection{The \Sphinxes extension for sets of nodes}

@@

\subsubsection{\Sphinxes algorithms and \acf*{SPOR}}

\Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates a header.

@@

We will synchronize our detailed descriptions with that of 
\ac{Sphinx}, hence we will use the following notation:
\begin{itemize}
  \item \(\kappa\) is the security parameter.
    The adversary must thus do about \(2^\kappa\) work to break the security.

@@

If \(L' = \{\rdvnode\}\), the packet payload contains another \Sphinxes packet 
to be forwarded.
Decrypt the payload \(\delta\) to get the mix packet \((M', \delta')\gets 
  \prp^{-1}(\hash_\prp(s_i), \delta)\).
Run the \(\ProcessHeader\) algorithm with \((M', \delta')\) and 
\(\ProcessMessage\) as input.

>>>>

\section{SphinxES: the Sphinx header format Extended for Sets of nodes}%
\label{SphinxES}

\Textcite{Sphinx} designed \iacadv{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
Sphinx only provides one node per onion layer; in this section we extend Sphinx 
to SphinxES, which allows for multiple nodes per onion layer.
As such, SphinxES could be described as a source-bounded random-walk protocol, 
\ie the each node selects the next node randomly from a set restricted by the 
source.

\subsection{Overview of the Sphinx header format}

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve SphinxES.
For a more detailed understanding of Sphinx, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

\subsection{The SphinxES extension for sets of nodes}

@@

\subsection{SphinxES algorithms}

SphinxES provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates a header.

@@

We will synchronize our detailed descriptions with that of 
Sphinx, hence we will use the following notation:
\begin{itemize}
  \item \(\kappa\) is the security parameter.
    The adversary must thus do about \(2^\kappa\) work to break the security.

@@

If \(L' = \{\rdvnode\}\), the packet payload contains another SphinxES packet 
to be forwarded.
Decrypt the payload \(\delta\) to get the mix packet \((M', \delta')\gets 
  \prp^{-1}(\hash_\prp(s_i), \delta)\).
Run the \(\ProcessHeader\) algorithm with \((M', \delta')\) and 
\(\ProcessMessage\) as input.

### 2020-03-27 spores-protocol-paper/approach.tex

\section{Overall approach}%
\label{approach}
Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name, they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and
some single-use reply mix-headers.
They use these reply headers to transfer the file contents of \(f\) over a 
network of unreliable nodes while also achieving privacy.

%% Figure~\ref{fig:outline} shows the components needed to obtain the
%% routing information for the headers.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  %  \import{figures/}{outline_figure_only.pdf_tex}
    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
    \caption{Architectural overview of the \ac{SPORES} private file sharing service.}
    \label{fig:outline}
\end{figure}

After the initial, out-of-band setup, file transfer happens along
onion routes with the following features:\\
\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. \\
 \textbf{Predictive.} The choice of which nodes is placed in which onion routing
  layer is informed on a predictive model for availability, disseminated
  by an overlay and queried by random peer sampling (RPS). Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route. This population is controlled by the random peer sampling service, which we assume is secure. This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
 \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.\\
 \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
  a source route and encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on the
  \ac{Sphinx} mix-header format, which we extend to allow for the
  changes above, described in \cref{Sphinxes}.

@@

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from \ac{Sphinx} and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
message-based (performance) communication.
But unlike \ac{Sphinx}, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

@@

Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
\commentFT{What follows seems quite convoluted, with a lot of repetition. Would be nice to revise.} As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

A device's availability depends on its user's behavior, hence the device must 
predict this behavior. This is best done jointly between all of the user's devices.
%In \cref{sec:squad_overlay}, we describe
Accordingly we introduce a protocol that allows the devices to 
compute their own availability prediction function based on the observations by 
all other devices.

Finally, we introduce the complete \ac{SPORES} protocol that acts as a private P2P file transfer. It 
allows the device \squad to act as an autonomous system.
In particular, we introduce a protocol which allows transferring larger 
messages by fragmentation and reassembly across the devices in the \squad  (Figure~\ref{fig:outline} \ding{204}).

>>>>

\section{Overall approach}%
\label{approach}
Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name, they start by sharing some information out-of-band, comparable 
to links for sharing a file in the Cloud.
More precisely, they exchange metadata on \(f\), encryption keys, and
some single-use reply mix-headers.
They use these reply headers to transfer the file contents of \(f\) over a 
network of unreliable nodes while also achieving privacy.

After the initial, out-of-band setup, file transfer happens along
onion routes with the following features:\\
\begin{description}
  \item[Stateless] There is no circuit creation.
    The protocol is stateless up to remembering previously seen packets to 
    prevent replay attacks.
    (There is no relation between packets.)

  \item[Probabilistic] Instead of source routes with one node per onion layer, 
    each layer consists of a set of nodes and although the source route still 
    determines the sequence of layers, the actual node used for the next hop of 
    forwarding is selected from the set in an ad-hoc way\daniel{%
      What is \enquote{ad-hoc way}?}, resulting in a source-bounded random 
    walk.

  \item[Onion Routing] Put simply, in onion routing, the sender creates a 
    source route and encapsulates the payload and next-hop information in 
    layers (by encryption), that are \emph{peeled} (decrypted) one by one along 
    the route. By virtue of these layers, the forwarding nodes on the route do 
    not know where on the route they are and thus whether they have received a 
    packet directly from the sender or some other intermediate node. We base 
    our format for layering and peeling on the \ac{Sphinx} mix-header format, 
    which we extend to allow for sets of nodes in each layer.
\end{description}

@@

As depicted in \cref{fig:outline}, \ac{SPORES} relies on a probabilistic onion 
routing protocol (\ac{SPOR}). \Ac{SPOR} in turn combines a set-based mix-header 
format (\Sphinxes) together with a node selection protocol.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from \ac{Sphinx} and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}, \cref{Sphinxes}) provides, just 
as \ac{Sphinx}, unidirectional (network structure), message-based (performance) 
communication.
But unlike \ac{Sphinx}, \Sphinxes is a hybrid: source-hop-by-hop routed, 
essentially a source-bounded random walk (communication model).
\Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme, this does not endanger the security
properties~\cite{CLOnionRouting}).

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  %  \import{figures/}{outline_figure_only.pdf_tex}
    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
    \caption{%
      Architectural overview of the \ac{SPORES} private file sharing service.
      \daniel{This figure must be updated.}
    }
    \label{fig:outline}
\end{figure}

@@

Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
The choice of this source of random nodes affects the network view (routing 
information) of each node, as well as how decentralized the scheme becomes and 
whether the network topology is fully, mostly or partly connected (network 
structure).

Each node must be associated with a public key and some prediction function.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the prediction 
function to optimize the properties of the entire route, \ie across layers.
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

Finally, we introduce the complete \ac{SPORES} protocol that allows 
transferring larger messages by fragmentation and reassembly across the devices 
in the \squad  (Figure~\ref{fig:outline} \ding{204}).

### 2020-03-27 spores-protocol-paper/related.tex

P2P file sharing has been researched extensively, with respect to aspects such 
as architecture (starting with the semi-centralized Napster, then decentralized 
Gnutella), availability and replication~\cite{replica}, scalability 
(Bittorrent~\cite{bittorrent-incentives}), anonymity 
(Freenet~\cite{Clarke:2001}, \ac{Tor}, and \acp{DHT} such as CAN, Chord, 
Pastry, and Tapestry, see~\cite{dhtchurn} for an overview). In contrast to our 
work, these efforts principally aimed at enabling dissemination to many users 
who do not necessarily know each other in person. With \ac{SPORES}, we focus on 
sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of 
users that out-of-band agree to share a file but do not keep it available for 
anyone else in the future.

@@

Onion routing schemes, with infrastructure and governance (\ac{Tor}) and 
without (I2P\footnote{https://geti2p.net/en/}), though geared toward web 
browsing, come closest to file transfer without third-party storage. They do 
not, however, allow for unreliable user devices as relay nodes, as we do.

>>>>

P2P file sharing has been researched extensively, with respect to aspects such 
as architecture (starting with the semi-centralized Napster, then decentralized 
Gnutella), availability and replication~\cite{replica}, scalability 
(Bittorrent~\cite{bittorrent-incentives}), anonymity 
(Freenet~\cite{Clarke:2001}, Tor, and \acp{DHT} such as CAN, Chord, 
Pastry, and Tapestry, see~\cite{dhtchurn} for an overview). In contrast to our 
work, these efforts principally aimed at enabling dissemination to many users 
who do not necessarily know each other in person. With \ac{SPORES}, we focus on 
sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of 
users that out-of-band agree to share a file but do not keep it available for 
anyone else in the future.

@@

Onion routing schemes, with infrastructure and governance (Tor) and 
without (I2P\footnote{https://geti2p.net/en/}), though geared toward web 
browsing, come closest to file transfer without third-party storage. They do 
not, however, allow for unreliable user devices as relay nodes, as we do.
